HTW Model e1

### 2024-03-25 Model/htw_model_e1.qmd
filling out missing parts and correcting plots

>>>>

 post_dat_l |> filter(Fit_Method=="Test_Train") |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvgE1$vb))) |>
  ggplot(aes(x=vbLab,y=dist,fill=Resp)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(~condit, axes = "all",ncol=2,scale="free")

 post_dat_l |> filter(Fit_Method=="Test_Train") |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvgE1$vb))) |>
  ggplot(aes(x=bandType,y=dist,fill=Resp)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(~condit, axes = "all",ncol=2,scale="free")

 post_dat_l |> filter(Fit_Method=="Test_Train") |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvgE1$vb))) |>
  ggplot(aes(x=Resp,y=dist,fill=bandType)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(~condit, axes = "all",ncol=2,scale="free")

 post_dat_l |> filter(Fit_Method=="Test_Train") |> 
  mutate(vbLab = factor(paste0(x,"-",x+200),levels=levels(testAvgE1$vb))) |>
  ggplot(aes(x=bandType,y=dist,fill=condit)) + 
  stat_bar + 
  #facet_wrap(~Resp)
  ggh4x::facet_nested_wrap(~Resp, axes = "all",ncol=3,scale="free")
